The Spine of American Legal Practice

### 2016-06-25 article/article.Rmd
Map with caption

@@

NY1850-554 | NY1850-555 | CA1851-001 | CA1851-002 |

|:----------|:----------:|:----------:|:----------:|:----------:|

|NY1850-554 | | 0 | 0.14 | 0 |

|NY1850-555 | | | 0 | 0.41 |

|CA1851-001 | | | | 0 |

|CA1851-002 | | | | |

As we would expect the first respective sections (New York § 554 and California § 1) have a score of 0.14, which indicates that they are similar but have significant differences, while the second sections (New York § 555 to California § 2) have a much higher similarity score since only a few words were changed. Just as important when we compare the first section in New York to the second section in California, we get a score of 0; the two sections are nothing like each other.

The aim, then, was to create a triangular matrix like the one above, but with approximately 98,000 rows and 98,000 columns, containing the similarity scores for each possible pair of sections. While this is easy enough to conceptualize, such a matrix is actually quite large, containing about 4.8 billion comparisons. This would take an unreasonable amount of computation time, and most of these comparisons would be unnecessary, since each section has no relationship to most other sections (like the matrix above, most scores will be zero). We therefore implemented the minhash/locality sensitive hashing (LSH) algorithm to detect candidate pairs, that is, documents which were likely to be matches, and then we measured the Jaccard score for only those candidate pairs.[^36]

>>>>

![This map shows which states adopted codes of civil procedure based on the New York Field Code. The date shown is the date of the first enactment of a procedure code; most states subsequently revised their codes. Note that many southern states and western states came to adopt the Field Code during the period of Greater Reconstruction. By the end of the nineteenth-century, thirty-one jurisdictions (those displayed on the map, plus Alaska) had adopted a version of the Field Code.](field-code-states-map.jpeg)

@@

|            | NY1850-554 | NY1850-555 | CA1851-001 | CA1851-002 |
|:-----------|:----------:|:----------:|:----------:|:----------:|
|NY1850-554  |            |          0 |       0.14 |          0 |
|NY1850-555  |            |            | 0          |       0.41 |
|CA1851-001  |            |            |            |          0 |
|CA1851-002  |            |            |            |            |

As we would expect the first respective sections (New York §554 and California §1) have a score of 0.14, which indicates that they are similar but have significant differences, while the second sections (New York §555 to California §2) have a much higher similarity score since only a few words were changed. Just as important, when we compare the first section in New York to the second section in California, we get a score of 0; the two sections are nothing like each other.

The aim, then, was to create a triangular matrix like the one above, but with approximately 98,000 rows and 98,000 columns, containing the similarity scores for each possible pair of sections. While this is easy enough to conceptualize, such a matrix is actually quite large, containing about 4.8 billion comparisons. This would take an unreasonable amount of computation time, and most of these comparisons would be unnecessary, since each section has no relationship to most other sections.

We therefore implemented the minhash/locality sensitive hashing (LSH) algorithm to detect pairs of possible matches. This algorithm

that is, documents which were likely to be matches, and then we measured the Jaccard score for only those candidate pairs.[^36]
